---
title: Poll Average in Gun Control
output:
  html_document: default
---
### Data 607 Assignment 1
### Eddie Xu

---
[link](https://projects.fivethirtyeight.com/guns-parkland-polling-quiz/)

### Introduction
Gun control is a polarizing topic in America, especially in 2018. The article cover the topic and presents the poll of Gun Control in America. Because of that, I want to find out about the average of adults and registered voter.

### Conclusion
Based on my analysis, it appears that registered voters are more vocal about gun control.

```{r}
### Load Libraries
library(ggplot2)
library(tidyverse)

```
### Read the CSV file
```{r}
readfile <- data.frame(read.csv("C:/Users/eddie/Data Science Project/607_assignment_1/poll-quiz-guns/guns-polls.csv"))
dim(readfile)
  
head(readfile)
```
### remove a column
```{r}
poll_df <- readfile %>% select(-c(URL))
head(poll_df)
```
### What is the poll support that are greater than 50?
```{r}
library(knitr)
Support_50 <- subset(poll_df, Support > 50)
Support_50

kable(Support_50, caption = "Poll Greater Than 50")
```
### Bar plot
### What is the poll average in gun control by Population?
```{r}
poll_average_df <- subset(poll_df, select = -c(Start, End, Pollster))
head(poll_average_df)

poll_average_df <- poll_average_df %>%
  select(Population, Support) %>%
  group_by(Population) %>%
  mutate(
    pop_avg = mean(Support)
  )

ggplot(poll_average_df, aes(Population, pop_avg, fill = Population)) + 
         geom_bar(stat = "identity", position = "dodge") +
         labs(title = "Poll Average in Population")
```